\begin{acknowledgments}

First and foremost, I would like to thank my advisors, Professors Louis F. DiMauro and Pierre Agostini for the opportunity to work on cutting edge research using world-class tools. They fostered a productive and collaborative environment from which I greatly benefited. Over the years, they gave invaluable feedback, asked probing questions, and drew upon their vast knowledge of physics to help me succeed.

I am also indebted to my colleagues and collaborators for their help throughout the years. Stephen Hageman designed major components of TABLe apparatus and assisted with nearly every single experiment; his insights regarding various experimental \& instrumental considerations undoubtedly improved the quality of my research. Andrew Piper designed the OMRON vacuum control system and developed an the interferometric stabilization scheme for the TABLe. Dietrich Kiesewetter coded the computer-motor interface and the homemade laser pointing software; he also helped with the initial design of the TABLe, hunted down sources of interferometric instability and made subtle improvements to the apparatus. Kent Talbert wrote the entire LabVIEW software data collection suite from scratch and provided numerous last-minute bug fixes and feature improvements. Dr. Antoine Camper implemented the phase plate \& phase grating, helped calibrate the photon spectrometer, and contributed to its early design. Sierra O'Bryan also worked on the initial optical design of the photon spectrometer. Dr. Yaguo Tang synthesized thin film germanium samples for ATAS experiments. Eric Moore automated the TABLe alignment system. Tim Gorman contributed to countless discussions about physics, experimental design and laser troubleshooting. And I would like to thank everyone else in the DiMauro group who has helped me throughout the years: Stephen Schoun, Dr. Tim Scarborough, Dr. Cosmin Blaga, Dr. Hyunwook Park, Dr. Junliang Xu, Urszula Szafruga, Kaikai Zhang, Kevin Gudenkauf, Zhou Wang, Yu Hang (Marco) Lai, Bryan Smith, Dr. Sha (Lisa) Li, Dr. Abraham Camacho, Daniel Tuthill, Dr. Vyacheslav (Slava) Leshchenko, and Dr. Li Fang.

Gratitude is also directed towards my collaborators. Jakub Husek, Dr. Anthony Cirri, Somnath Biswas \& Prof. Robert Baker from the OSU Chemistry Department joined many useful discussions pertaining to data collection, experimental design and sample considerations. Dr. Drake Austin performed the Keldysh ionization simulations and helped me understand some of the finer points of the Keldysh model; thanks go to Prof. Enam Chowdhury for arranging this collaboration. Dr. Christian Ott designed the original ``cage and crank" vacuum flange manipulator which was adapted to work with our photon spectrometer. Michael Chilcote, Michael Newburger, Jinsong Xu \& Yutichai Mueanngern from OSU, Prof. S.K. Sundaram from Alfred University, Dr. Grant Johnson, Dr. Venkateshkumar (Venky) Prabhakaran, Dr. Le Wang \& Dr. Yingge Du from PNNL provided samples for ATAS measurements. Marieke Jager from the Leone group and Norman Niewrzella from the Semiconductor Manufacturing Technology Business Group at Carl Zeiss SMT GmbH helped with the design of the ellipsoidal mirror. Rich Pfisterer, Ryan Irvin and Donna Pfisterer from Photon Engineering provided a university gratis software license of FRED, and answered questions about using the software.

I could not have achieved a fraction of what I've accomplished without the OSU support staff. Pete Gosser and Michael Graham of the Physics Machine Shop manufactured countless parts (including our vacuum chambers) and provided consulting about general machining practices and mechanical design. Special thanks go to Jon Shover from the Astronomy Machine Shop for welding the vacuum chambers and the high pressure cell. Phil Davids and Mark Reed helped out with general facility issues and logistics. Kent Ludwig repaired and improved our rough vacuum system. Kris Dunlap, Mary Kay Jackson, Shirley McClung, Dameyon Shipley, Kyle Schechter \& Jessica Middleton helped with administrative issues.

Last but not least, I'd like to recognize those who encouraged me to attend graduate school: Prof. Meigan Aronson, Dr. Jack Simonson, Dr. Jacob E. Grose, and Carlos Marques. In particular, I'd like to thank Prof. Aronson and Dr. Simonson for their mentorship during my time at Brookhaven National Laboratory. They set me down this path and I thank them for it.

\end{acknowledgments}